MRD_final_microbiome

### 2019-06-25 import_popln_data.Rmd
updated

setwd("~/globalmicrobiome")
mnd.incidence <- read_csv("mnd.csv",col_names = TRUE)
mnd.incidence <- as.data.frame(mnd.incidence)

@@

temp <- mb.gather(mnd.incidence)

>>>>

@@

setwd("~/globalmicrobiome")
# files nwed to be in the owrking directory
mnd.incidence <- read_csv("MND-De-B.csv",col_names = TRUE)
mnd.incidence <- as.data.frame(mnd.incidence)
temp <- mb.gather(mnd.incidence)
